Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-13 report/report.tex
Remove commented out toc
Fix headlines

%\newpage
%\setlength{\parskip}{0em}
%\tableofcontents
%\setlength{\parskip}{1em}
%\newpage

@@

\subsection{Research Question}

@@

\subsection{Evaluation}

@@

\subsection{Implementation overview}

\subsubsection{Assesment of Geodata Precision}

@@

\subsubsection{Collision study}

@@

\subsection{Problem Constraints}

@@

\section{Background}

\subsection{Background of 3D City Representation}

@@

\subsection{Related work}
When assessing the completeness of geodata, a very common scale is Van Oorts criteria for evaluating the quality of geographical information, which at the time of publication received attention from surveyors and cartographers. (van Oort, 2006) Since then a number of publications have examined slices of geodata from van Oort's criteria. In 2008, (Haklay, 2010) conducted such a study to estimate of the quality of OSM positional geodata in London and England. Since the OSM project started in London it was thought that OSM data in the London metropolitan area would be representative of the highest quality data available, and therefore a good indicator for the whole global OSM dataset. The study was conducted by comparing OSM data to Ordnance Survey datasets. The study showed that the OSM dataset had a rough positional accuracy of 6 meters from the reference dataset. However, at the time of the study, the OSM project had captured roughly 29\% of the area of England, meaning that the data completeness was fairly low.

@@

\section{The geodata used in this project}

@@

\subsection{OSM Data}

@@

\subsection{SLU Data}

@@

\subsection{A word on coordinate systems}

@@

\subsection{Specific preprocessing for SLU and OSM geodata}

@@

\section{Implemenation: Evaluation of the quality of geodata}

@@

\subsection{The accuracy classes that will not be focused on}

@@

\subsection{Assesment of dataset completeness}

@@

\subsection{Correspondence by building area}

@@

\subsection{Shape accuracy definition}

@@

\subsection{Closest point and point proximity}

@@

\section{Implementation: Collision study}

@@

\section{Results and metrics}

\subsection{Positional accuracy statistics}

@@

\subsection{Road collision study}

@@

\subsection{Completeness by building area}

@@

\subsection{Building matching statistics}

@@

\subsection{Shape accuracy statistics}

@@

\section{Analysis and Future Work}

\subsection{Quality of the OSM dataset}

@@

% Wednesday:
% TODO: Apply KTH thesis format
% TODO: Bold research questions
% TODO: Merge 2.1, 2.2
% TODO: 2.1: Add a sentence about where the question fits into the big picture
% TODO: 2.1: Add section refereces to implementation and results of the sub-questions
% TODO: Reduce long section headlines
% TODO: Rename analysis -> conclusions
% TODO: Shorten abstract
% TODO: Verify that citings look correct (compare to other reports)

@@

@@

\subsection{Suggested algorithms for correcting feature overlap}

@@

\subsection{Utility in real world applications}

>>>>

@@

\section{Research Question}

@@

\section{Evaluation}

@@

\section{Implementation overview}

\subsection{Assesment of Geodata Precision}

@@

@@

\section{Problem Constraints}

@@

\chapter{Background}

\section{Background of 3D City Representation}

@@

\section{Related work}
When assessing the completeness of geodata, a very common scale is Van Oorts criteria for evaluating the quality of geographical information, which at the time of publication received attention from surveyors and cartographers. (van Oort, 2006) Since then a number of publications have examined slices of geodata from van Oort's criteria. In 2008, (Haklay, 2010) conducted such a study to estimate of the quality of OSM positional geodata in London and England. Since the OSM project started in London it was thought that OSM data in the London metropolitan area would be representative of the highest quality data available, and therefore a good indicator for the whole global OSM dataset. The study was conducted by comparing OSM data to Ordnance Survey datasets. The study showed that the OSM dataset had a rough positional accuracy of 6 meters from the reference dataset. However, at the time of the study, the OSM project had captured roughly 29\% of the area of England, meaning that the data completeness was fairly low.

@@

\chapter{The geodata used in this project}

@@

\section{OSM Data}

@@

\section{SLU Data}

@@

\section{A word on coordinate systems}

@@

\section{Specific preprocessing for SLU and OSM geodata}

@@

\chapter{Implemenation: Evaluation of the quality of geodata}

@@

\section{The accuracy classes that will not be focused on}

@@

\section{Assesment of dataset completeness}

@@

\section{Correspondence by building area}

@@

\section{Shape accuracy definition}

@@

\section{Closest point and point proximity}

@@

\chapter{Implementation: Collision study}

@@

\chapter{Results and metrics}

\section{Positional accuracy statistics}

@@

\section{Road collision study}

@@

\section{Completeness by building area}

@@

\section{Building matching statistics}

@@

\section{Shape accuracy statistics}

@@

\chapter{Analysis and Future Work}

\section{Quality of the OSM dataset}

@@

% Wednesday:
% TODO: Bold research questions
% TODO: Merge 2.1, 2.2
% TODO: 2.1: Add a sentence about where the question fits into the big picture
% TODO: 2.1: Add section refereces to implementation and results of the sub-questions
% TODO: Reduce long section headlines
% TODO: Rename analysis -> conclusions
% TODO: Shorten abstract
% TODO: Verify that citings look correct (compare to other reports)

@@

\section{Collision study}

@@

\section{Suggested algorithms for correcting feature overlap}

@@

\section{Utility in real world applications}
